The Place of the Local Group in the Cosmic Web

### 2014-05-23 paper/main.tex
new text, new plots, clear trends

\title{The Place of the Local Group in the Cosmic Web}
\author{J. E. Forero-Romero$^1$, and R. Gonz\'alez$^2$}
\affil{$^1$ Departamento de F\'{i}sica, Universidad de los Andes,
  Cra. 1 No. 18A-10, Edificio Ip, Bogot\'a, Colombia\\
  $^2$ Instituto de Astrofísica, Pontificia Universidad Cat\'olica,
  Av. Vicu\~na Mackenna 4860, Santiago, Chile\\  
}
\email{je.forero@uniandes.edu.co}

@@

The algorithm to compute the potential is grid based. First we
interpolate the density into a cubic grid with a Cloud-In-Cell (CIC)
scheme and smooth it with a gaussian kernel. Then we obtain the
gravitational potential using FFT methods and use finite differences
to compute the Hessian at every point in the grid. In our case we have
used a grid size on and a gaussian smoothing with two times larger as
the typical separation between the two halos in the Local Group. The
purpose of this choice is to have both halos in the pair a common
environment. In this paper we use a grid spacing of $s=1.024$ \hMpc,
corresponding to a $256^3$ grid in the Bolshoi volume. The scale for
the gaussian smoothing uses the same value.

@@

We define two samples according to the tolerance in the selection constraints:
A sample named $2\sigma$, correspondig to LG analogues constrained by
two times the observational errors in the orbital values (radial
velocity, tangential velocity, and separation), and a more relaxed
sample named $3\sigma$ for LG analogues constrained by three times
observational errors accordingly. The number of pairs in each sample
is $46$ and $120$ respectively, notice we have less pairs than in
\citet{lganalogues} results, since we removed pairs which are too
close at $z=0$, i.e. their virial radii overlaps, also we removed a
couple pairs who merged or change their mass more than $20\%$ at
present time since they were detected at $z<0.1$.  We also have a
general sample which...

@@

\begin{figure*}
\begin{center}
  \includegraphics[width=0.48\textwidth]{alignments_e3_filament.pdf} 
  \includegraphics[width=0.48\textwidth]{alignments_e3_sheet.pdf} 
\end{center}
\caption{Cumulative distributions for the alignment between the normal
  vector $\hat{n}$ and the third eigenvector $\vec{e}_3$.
    \label{fig:alignment}}  
\end{figure*}

@@

The situation in the restricted $2\sigma$ and $3\sigma$ samples is very
different. By large the LGs in these samples are located in
filaments and sheets. In both samples, $\sim 50\%$ of the
pairs can be found in filaments while $\sim 40\%$ are in
in sheets.

These absolute numbers in each environment for each sample are
presented in Table \ref{table:web_type}.

@@

>>>>

\title{The Place of the Local Group in the Cosmic Web}
\author{J. E. Forero-Romero$^1$ and R. Gonz\'alez$^2$}
\affil{$^1$ Departamento de F\'{i}sica, Universidad de los Andes,
  Cra. 1 No. 18A-10, Edificio Ip, Bogot\'a, Colombia\\
  $^2$ Instituto de Astrofísica, Pontificia Universidad Cat\'olica,
  Av. Vicu\~na Mackenna 4860, Santiago, Chile\\  
}
\email{je.forero@uniandes.edu.co}

@@

The algorithm to compute the potential is grid based. First we
interpolate the density into a cubic grid with a Cloud-In-Cell (CIC)
scheme and smooth it with a gaussian kernel. Then we obtain the
gravitational potential using FFT methods and use finite differences
to compute the Hessian at every point in the grid. In our case we have
used a grid size on and a gaussian smoothing with two times larger as
the typical separation between the two halos in the Local Group. The
purpose of this choice is to have both halos in the pair a common
environment. In this paper we use a grid spacing of $s=0.97$ \hMpc,
corresponding to a $256^3$ grid in the Bolshoi volume. The scale for
the gaussian smoothing uses the same value.

@@

We define two samples according to the tolerance in the selection constraints:
A sample named $2\sigma$, correspondig to LG analogues constrained by
two times the observational errors in the orbital values (radial
velocity, tangential velocity, and separation), and a more relaxed
sample named $3\sigma$ for LG analogues constrained by three times
observational errors accordingly. The number of pairs in each sample
is $46$ and $120$ respectively, notice we have less pairs than in
\citet{lganalogues} results, since we removed pairs which are too
close at $z=0$, i.e. their virial radii overlaps, also we removed a
couple pairs that merged or change their mass more than $20\%$ at
present time since they were detected at $z<0.1$.

We also have a third general sample that we use as a control for our
results. {\bf What are the criteria for this sample?}

@@

\begin{figure*}
\begin{center}
  \includegraphics[width=0.48\textwidth]{alignments_e1_filament.pdf} 
  \includegraphics[width=0.48\textwidth]{alignments_e1_sheet.pdf} 
  \includegraphics[width=0.48\textwidth]{alignments_e2_filament.pdf} 
  \includegraphics[width=0.48\textwidth]{alignments_e2_sheet.pdf} 
  \includegraphics[width=0.48\textwidth]{alignments_e3_filament.pdf} 
  \includegraphics[width=0.48\textwidth]{alignments_e3_sheet.pdf} 
\end{center}
\caption{Cumulative distributions for the alignment between the unit
  vector linking the two halos, $\hat{r}$, and the eigenvectors
  defining the cosmic web.
    \label{fig:alignment}}  
\end{figure*}

@@

The situation in the restricted $2\sigma$ and $3\sigma$ samples is very
different. By large the LGs in these samples are located in
filaments and sheets. In both samples, $\sim 50\%$ of the
pairs can be found in filaments while $\sim 40\%$ are in
in sheets. These absolute numbers in each environment for each sample
are presented in Table \ref{table:web_type}.

@@

We now explore the alignment of the pairs with respect to the cosmic
web. First we define the unit vector $\hat{r}$ that links the two
halos. Then, we compute the dot product of $\hat{r}$ and each one of
the three eigenvectors for pair in the three samples. In Figure
\ref{fig:alignment} we show the main result of that study, it
presents the cumulative distribution of
$\mu\equiv\hat{e}_3\cdot\hat{r}$ for pairs located in filaments and
sheets. The straight line corresponds to the expected result for a
random vector distribution.

From this Figure we first see that there is a clear distinct behavior
between the general samples and the 3$\sigma$-2$\sigma$ samples. The
general sample tenst to be aligned along the $\hat{e}_3$ vector, the
3$\sigma$ sample does not show any strong alignment and the 2$\sigma$
pairs tend to be perpendicular to the $\hat{e}_3$ vector and slightly
parallel to $\hat{e}_1$. These trends hold in filaments and walls.

Let's focus on filaments first. That result means that in the general
sample the two halos tend to lie along the filament, while in the
2$\sigma$-3$\sigma$ samples they are located perpendicular to the
filament. If one considers that in these samples the motion is radial,
that means that the pairs are moving into the filament.

In the case of sheets, the pairs in the general sample tend to lie on
the sheet plane along the direction of the slowest collapsing
direction. In the 2$\sigma$ samples the pairs are not constrained to
the plane anymore and are perpendiculat to the $\hat{e}_3$
vector. Considering the preferential radial motion of these pairs,
that mens that the pairs are moving into the pancake all over a plane that
is itself perpendicular to the sheet.
